BurgerMax Presents: OpenAdcess

### 2017-03-01 digital-library.tex
Misc fill ins

The free tier will only allow downloads at \todo{rate} and no more than one
paper download per day.
Additionally, the user will be required to watch an upgrade screen
\todo{explain this} count down for 10 minutes before the download button is
clickable.
If the website loses focus, the counter will be restarted.
The \premium tier will cost \todo{rate} but will allow unlimited downloads and
will not be rate limited.

>>>>

The free tier will only allow downloads at slow speeds and no more than one
paper per day.
Additionally, the user will be required to stare at a screen compelling them to
upgrade while a counter decrements for 10 minutes before the download button is
clickable.
If the website loses focus, the counter will be restarted.
The \premium tier will allow unlimited downloads and will not be rate limited.

### 2017-03-01 paper-sponsorships.tex
Misc fill ins

\subsection{Native Ads}
\todo{Define native advertising}

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads are to be native, an advertisement that is recognizable as an ad
will result in a strong reject of the paper.
The ad section must be at least one page long, but there is upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

\subsection{Investor Author Dispute Settlement}
We have founded an Investor Author Dispute Settlement (IADS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle will dash the hopes of the typical \todo{brand}
consumer.
Moreover, since \todo{brand} owns both of these complexity classes as defined
in section \todo{ref branded objects section} their assets will lose value and
this loss must be compensated by the ``bloggers".

% TODO: Reference this:
% http://www.cs.utexas.edu/users/EWD/transcriptions/EWD07xx/EWD743.html
\subsection{Branded mathematical objects}
\label{sec:brands}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

@@

@@

\paragraph{Dropped Packets}
Dropped Packets serves as the traditional missed connections section of the
classifieds.
While this could be used to contact that cutie \todo{sp?} from the latest
conference, we believe that it could also be used to publicly shame those who
miss meetings.
For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!"

>>>>

\subsection{Native Ads}
Native advertisements are advertisements meant to be disguised among the normal
content of a publication.
They are written in the same style as the publication and appear alongside
unsponsored content in an attempt to make the reader believe that they are
reading the original publication and not an advertisement \cite{native}.

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads are to be native, an advertisement that is recognizable as an ad
will result in a strong reject of the paper.
The ad section must be at least one page long, but there is no upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

\subsection{Branded mathematical objects}
\label{sec:brands}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

@@

\subsection{Investor Author Dispute Settlement}
We have founded an Investor Author Dispute Settlement (IADS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle will dash the hopes of the typical Sparrow Soap
consumer they may use the IADS court to mitigate their losses from this
finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the ``bloggers."

@@

\paragraph{Dropped Packets}
Dropped Packets serves as the traditional missed connections section of the
classifieds.
While this could be used to contact that cutie from the latest conference, we
believe that it could also be used to publicly shame those who miss meetings.
For example, ``Damn it Dave, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!"
